Data Analysis

### 2024-03-26 ms1_data_analysis.Rmd
Breaking code into components and integrating in the markdown file.
Latest version of the manuscript, code and cleanup.

First we analyze only traits ignoring location. Later we can mak an attempt to see wether importance of

@@

@@

source('code/model_definitions_pgls.R')

@@

# 1. Full model (quadratic, and site interactions) vs no traits
# anova(no.traits, full.model)            # full model is better

@@

# 2.1 Remove SLA
# anova(full.model, q.herb.q.water) # no-difference, keep model without the SLA a simpler model?
# 2.2 Remove herbivory
# anova(full.model, q.sla.q.water.noint) # Model without herbivory is significantly worse
# 2.3 Remove water content?
# anova(full.model, q.sla.q.herb) # Model without water is significantly worse

# Herbivory and water are the most important!!!

# 3. Reduce model even further - 1 trait models.
# anova(q.herb.q.water, just.sla.quadratic)   # Two trait model better
# anova(q.herb.q.water, just.herb.quadratic)  # Two trait model better
# anova(q.herb.q.water, just.water.quadratic) # Two trait model better

# 4. Quadratic vs linear
# anova(q.herb.q.water, l.herb.l.water) # Quadratic model is still better

# 5. Interaction reduction
# anova(q.herb.q.water, q.herb.q.water.noint) # Model with interaction is better
# anova(q.herb.q.water, just.water.quadratic.noint) # Model with interaction is better
# anova(q.herb.q.water, just.water.linear.noint)

@@

```{r, results='asis'}
# So the best model is the one without the traits!
# tab_model(q.herb.q.water)
# tab_model(just.water.quadratic.noint)
i.mod <- q.herb.q.water
i.dD <- deltaData
```

@@

@@

source('code/model_definitions_pgls.R')

@@

# 1. Full model (quadratic, and site interactions) vs no traits
# anova(no.traits, full.model)            # full model is better

# Both q.herb.q.water and q.sla.q.water are simpler, but which one is better?
# anova(full.model, q.sla.q.herb) # Model without water is significantly worse

# 2.3 Remove water content?
# anova(full.model, q.sla.q.herb) # Model with herbivory is much better!
# Water is important!!!

# anova(q.herb.q.water, q.sla.q.water) # q.sla.q.water is better based on AIC

# 3. Reduce model even further - 1 trait models.
# anova(q.sla.q.water, just.sla.quadratic)  # q.sla.q.water is still better
# anova(q.sla.q.water, just.herb.quadratic) # q.sla.q.water is still better
# anova(q.sla.q.water, just.water.quadratic) # model with just water is as good as q.sla.q.water

# model with just water is not different form the full model, and it has lower AIC

# 4. Quadratic vs linear
# anova(just.water.quadratic, just.water.linear) # Linear is simpler model still better

# 5. Interaction reduction
# anova(just.water.linear, just.water.linear.noint) # Interaction does not bring anything to the model

@@

# So the best model is the one with only water!
# tab_model(just.water.linear.noint)
f.mod <- just.water.linear.noint
f.dD <- deltaData
```

@@

@@

```{r, results='asis'}
# So the best model is ... !
# tab_model(just.water.linear)
h.mod <- just.water.linear
h.dD <- deltaData
```

@@

@@

# 2.1 Remove SLA
# anova(full.model, q.herb.q.water) # Full model is significanlty better

# 2.2 Remove herbivory
# anova(full.model, q.sla.q.water.noint) # Full model still better

# 2.3 Remove water content?
# anova(full.model, q.sla.q.herb) # Full model still better

# 3. Reduce model even further - 1 trait models.
# anova(full.model, just.sla.quadratic)
# anova(full.model, just.herb.quadratic)
# anova(full.model, just.water.quadratic)

# 4. Quadratic vs linear
# anova(full.model, all.linear) # Full model still better

# 5. Interaction reduction
# anova(full.model, full.model.noint) # Full model still better
```

@@

tab_model(p.mod, i.mod, h.mod, f.mod,
          pred.labels = c("Intercept", 
                          "Log[SLA]-linear", 
                          "Numba", 
                          "Yawan",
                          "Log[SLA]-quadratic", 
                          "Water content - linear", 
                          "Water content - quadratic",
                          "Herbivory [%] - linear",
                          "Herbivory [%] - quadratic",
                          "Species richness",
                          "Abundance",
                          "LRR SLA",
                          "Log[SLA]-linear : Numba",
                          "Log[SLA]-linear : Yawan",
                          "Log[SLA]-quadratic : Numba",
                          "Log[SLA]-quadratic : Yawan",
                          "Water content-linear : Numba",
                          "Water content-linear : Yawan",
                          "Water content-quadratic : Numba",
                          "Water content-quadratic : Yawan",
                          "Herbivory-linear : Numba",
                          "Herbivory-linear : Yawan",
                          "Herbivory-quadratic : Numba",
                          "Herbivory-quadratic : Yawan"),
          dv.labels = c("Predator", "Insecticide", "Extra herbivory", "Fungicide"),
          string.pred = "Coeffcient",
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value")

>>>>

First we analyze only traits ignoring location. Later we can make an attempt to see wether importance of

@@

### Are there differences in trait values between elevations?

logit <- function(p){
  return(log(p/(1-p)))
}

trait_data <- data.woody.brut %>%
         mutate(fsite = factor(site, levels=c("wanang","numba","yawan")),
                perc_wc = water.cont/wet_leafg) %>%
         filter(treatment == "c",
                perc_wc > 0,
                unified_names != "piper_aduncum")

sla_plot <- ggplot(trait_data, aes(y=log(sla.d.m2kg1), x = fsite)) +
  geom_jitter(alpha = 0.3,pch=19) +
  theme_classic() + ggtitle("SLA")
wc_plot <- ggplot(trait_data, aes(y=logit(perc_wc), x = fsite)) +
  geom_jitter(alpha = 0.3,pch=19) +
  theme_classic()+ ggtitle("Logit[proportional water content]")

jpeg('figures/sla_wc_elevation.jpg')
ggpubr::ggarrange(sla_plot, wc_plot)
dev.off()
```

```{r}
# test with pgls model

trait_data_tl <- trait_data %>%
  filter(unified_names %in% myTree.rand.poly$tip.label)

trait_elevation_model <- gls(
    log(sla.d.m2kg1) ~ fsite,
    data = trait_data_tl,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

trait_elevation_model2 <- gls(
    logit(perc_wc) ~ fsite,
    data = trait_data_tl,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# summary(trait_elevation_model)
# plot(trait_elevation_model) # better fit for log

posthoc_test <- predictmeans::predictmeans(trait_elevation_model, "fsite", adj='tukey')$mean_table$Table

posthoc_test2 <- predictmeans::predictmeans(trait_elevation_model2, "fsite", adj='tukey')$mean_table$Table

sla_ph <- ggplot(as.data.frame(posthoc_test), aes(x = fsite, y = Mean)) +
  geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=.05) +
  geom_point()

wc_ph <- ggplot(as.data.frame(posthoc_test2), aes(x = fsite, y = Mean)) +
  geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE), width=.05) +
  geom_point()

ggpubr::ggarrange(sla_ph, wc_ph, labels = c("SLA", "WC"))

@@

```{r}
source('code/model_definitions_pgls_no_herb.R')

moddata_w <- moddata[moddata$site == "wanang", ]
moddata_n <- moddata[moddata$site == "numba", ]
moddata_y <- moddata[moddata$site == "yawan", ]

null_w <- gls(
    lrrtb ~ 1,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_w <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_n <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_y <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_mse <- mean(just_traits_w$residuals^2)
numba_mse <- mean(just_traits_n$residuals^2)
yawan_mse <- mean(just_traits_y$residuals^2)

# MSE for models with traits and all other descriptors
full_model_w <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_n <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_y <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# MSE for models without the traits but all other descriptors
desc_model_w <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_n <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_y <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_full_mse <- mean(full_model_w$residuals^2)
numba_full_mse <- mean(full_model_n$residuals^2)
yawan_full_mse <- mean(full_model_y$residuals^2)

# Compare MSE only models with desc
wanang_desc_mse <- mean(desc_model_w$residuals^2)
numba_desc_mse <- mean(desc_model_n$residuals^2)
yawan_desc_mse <- mean(desc_model_y$residuals^2)

mse_data_i = data.frame(Site = factor(c("Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan"),levels = c("Wanang", "Numba", "Yawan")),
           MSE = c(wanang_mse, numba_mse,yawan_mse,                          
                   wanang_full_mse, numba_full_mse, yawan_full_mse,
                   wanang_desc_mse, numba_desc_mse, yawan_desc_mse),
           Model = c("Traits","Traits","Traits",
                     "Traits+Descriptors","Traits+Descriptors","Traits+Descriptors",
                     "Descriptors","Descriptors","Descriptors"),
           Treatment = "Insecticide")

ggplot(mse_data_i, aes(x = Site, y = MSE, fill = Model))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_bw() + ggtitle("Insecticide")

```{r}
# 
# 
# just_traits_w_l <- gls(
#     lrrtb ~ sla.d.m2kg1 + water.cont,
#     data = moddata_w,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_sla_w <- gls(
#     lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2),
#     data = moddata_w,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_sla_w_l <- gls(
#     lrrtb ~ sla.d.m2kg1,
#     data = moddata_w,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_wc_w <- gls(
#     lrrtb ~ water.cont + I(water.cont^2),
#     data = moddata_w,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_wc_w_l <- gls(
#     lrrtb ~ water.cont,
#     data = moddata_w,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# 
# # Traits are better
# anova(null_w, just_traits_w)
# 
# # Quadratic + two traits is better
# anova(just_traits_w, just_traits_w_l)
# anova(just_traits_w, just_sla_w)
# anova(just_traits_w, just_wc_w)
# anova(just_traits_w, just_sla_w_l)
# anova(just_traits_w, just_wc_w_l)
# 
# RsquareAdj(just_traits_w)
# 
# sjPlot::tab_model(just_traits_w,
#                   just_traits_w_l)
# 
#

# All sites
# 
# null_traits <- gls(
#     lrrtb ~ 1,
#     data = moddata,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   ) 
# 
# just_traits.q.no_int <- gls(
#     lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
#     data = moddata,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# 
# just_traits.l.no_int <- gls(
#     lrrtb ~ sla.d.m2kg1 + water.cont,
#     data = moddata,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_traits.q <- gls(
#     lrrtb ~ sla.d.m2kg1 * site + 
#       I(sla.d.m2kg1^2) * site + 
#       water.cont * site + 
#       I(water.cont^2) * site,
#     data = moddata,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# 
# just_traits.l <- gls(
#     lrrtb ~ sla.d.m2kg1 * site + water.cont *  site,
#     data = moddata,
#     method = "ML",
#     correlation = corMartins(2.718282,
#                              phy = myTree.rand.poly,
#                              form = ~unified_names,
#                              fixed = T),
#     na.action = na.omit
#   )
# 
# just_sla.q
# 
# sjPlot::tab_model(just_traits)

```{r, results='asis'}
# Are traits improving the null model

@@

# 1. Full model (quadratic, and site interactions) vs no traits
anova(no.traits, full.model)            # full model is better

@@

# 2.1 Remove SLA
anova(full.model, just.water.quadratic) # full_model

# 2.3 Remove water content?
anova(full.model, just.sla.quadratic) # No significant difference

# 4. Quadratic vs linear
anova(just.sla.quadratic, just.sla.linear) # Quadratic model is still better

# 5. Interaction reduction
anova(just.sla.quadratic, just.sla.quadratic.noint) # Model with interaction is better

@@

```{r, results='asis'}
# So the best model is the one without the traits!
# tab_model(q.herb.q.water)
# tab_model(just.water.quadratic.noint)
i.mod <- just.sla.quadratic
i.dD <- deltaData
```

@@

source('code/model_definitions_pgls_no_herb.R')

moddata_w <- moddata[moddata$site == "wanang", ]
moddata_n <- moddata[moddata$site == "numba", ]
moddata_y <- moddata[moddata$site == "yawan", ]

null_w <- gls(
    lrrtb ~ 1,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_w <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_n <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_y <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_mse <- mean(just_traits_w$residuals^2)
numba_mse <- mean(just_traits_n$residuals^2)
yawan_mse <- mean(just_traits_y$residuals^2)

# MSE for models with traits and all other descriptors
full_model_w <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_n <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_y <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# MSE for models without the traits but all other descriptors
desc_model_w <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_n <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_y <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_full_mse <- mean(full_model_w$residuals^2)
numba_full_mse <- mean(full_model_n$residuals^2)
yawan_full_mse <- mean(full_model_y$residuals^2)

# Compare MSE only models with desc
wanang_desc_mse <- mean(desc_model_w$residuals^2)
numba_desc_mse <- mean(desc_model_n$residuals^2)
yawan_desc_mse <- mean(desc_model_y$residuals^2)

mse_data_f = data.frame(Site = factor(c("Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan"),levels = c("Wanang", "Numba", "Yawan")),
           MSE = c(wanang_mse, numba_mse,yawan_mse,                          
                   wanang_full_mse, numba_full_mse, yawan_full_mse,
                   wanang_desc_mse, numba_desc_mse, yawan_desc_mse),
           Model = c("Traits","Traits","Traits",
                     "Traits+Descriptors","Traits+Descriptors","Traits+Descriptors",
                     "Descriptors","Descriptors","Descriptors"),
           Treatment = "Fungi")

ggplot(mse_data_f, aes(x = Site, y = MSE, fill = Model))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_bw() + ggtitle("Fungi")

@@

source('code/model_definitions_pgls_no_herb.R')

@@

# 1. Full model (quadratic, and site interactions) vs no traits
anova(no.traits, full.model)            
# model with traits does not have a significantly higher likelihood.

@@

# So the best model is the one with only water!
# tab_model(just.water.linear.noint)
f.mod <- no.traits
f.dD <- deltaData
```

@@

source('code/model_definitions_pgls_no_herb.R')

moddata_w <- moddata[moddata$site == "wanang", ]
moddata_n <- moddata[moddata$site == "numba", ]
moddata_y <- moddata[moddata$site == "yawan", ]

null_w <- gls(
    lrrtb ~ 1,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_w <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_n <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_y <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_mse <- mean(just_traits_w$residuals^2)
numba_mse <- mean(just_traits_n$residuals^2)
yawan_mse <- mean(just_traits_y$residuals^2)

# MSE for models with traits and all other descriptors
full_model_w <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_n <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_y <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# MSE for models without the traits but all other descriptors
desc_model_w <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_n <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_y <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_full_mse <- mean(full_model_w$residuals^2)
numba_full_mse <- mean(full_model_n$residuals^2)
yawan_full_mse <- mean(full_model_y$residuals^2)

# Compare MSE only models with desc
wanang_desc_mse <- mean(desc_model_w$residuals^2)
numba_desc_mse <- mean(desc_model_n$residuals^2)
yawan_desc_mse <- mean(desc_model_y$residuals^2)

mse_data_h = data.frame(Site = factor(c("Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan"),levels = c("Wanang", "Numba", "Yawan")),
           MSE = c(wanang_mse, numba_mse,yawan_mse,                          
                   wanang_full_mse, numba_full_mse, yawan_full_mse,
                   wanang_desc_mse, numba_desc_mse, yawan_desc_mse),
           Model = c("Traits","Traits","Traits",
                     "Traits+Descriptors","Traits+Descriptors","Traits+Descriptors",
                     "Descriptors","Descriptors","Descriptors"),
           Treatment = "Herbivore")

ggplot(mse_data_h, aes(x = Site, y = MSE, fill = Model))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_bw() + ggtitle("Herbivore")

@@

```{r, results='asis'}
# So the best model is ... !
# tab_model(just.water.linear)
h.mod <- no.traits
h.dD <- deltaData
```

@@

source('code/model_definitions_pgls_no_herb.R')

moddata_w <- moddata[moddata$site == "wanang", ]
moddata_n <- moddata[moddata$site == "numba", ]
moddata_y <- moddata[moddata$site == "yawan", ]

null_w <- gls(
    lrrtb ~ 1,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_w <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_n <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

just_traits_y <- gls(
    lrrtb ~ sla.d.m2kg1 + I(sla.d.m2kg1^2) + water.cont + I(water.cont^2),
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_mse <- mean(just_traits_w$residuals^2)
numba_mse <- mean(just_traits_n$residuals^2)
yawan_mse <- mean(just_traits_y$residuals^2)

# MSE for models with traits and all other descriptors
full_model_w <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_n <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

full_model_y <- gls(
    lrrtb ~ lsla.d + I(lsla.d^2) + water.cont + I(water.cont^2) +
      richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# MSE for models without the traits but all other descriptors
desc_model_w <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_w,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_n <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_n,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

desc_model_y <- gls(
    lrrtb ~ richness + labu + lrrsla + lrrwtrc,
    data = moddata_y,
    method = "ML",
    correlation = corMartins(2.718282,
                             phy = myTree.rand.poly,
                             form = ~unified_names,
                             fixed = T),
    na.action = na.omit
  )

# Compare MSE only models with quadratic and 
wanang_full_mse <- mean(full_model_w$residuals^2)
numba_full_mse <- mean(full_model_n$residuals^2)
yawan_full_mse <- mean(full_model_y$residuals^2)

# Compare MSE only models with desc
wanang_desc_mse <- mean(desc_model_w$residuals^2)
numba_desc_mse <- mean(desc_model_n$residuals^2)
yawan_desc_mse <- mean(desc_model_y$residuals^2)

mse_data_p = data.frame(Site = factor(c("Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan",
                    "Wanang", "Numba", "Yawan"),levels = c("Wanang", "Numba", "Yawan")),
           MSE = c(wanang_mse, numba_mse,yawan_mse,                          
                   wanang_full_mse, numba_full_mse, yawan_full_mse,
                   wanang_desc_mse, numba_desc_mse, yawan_desc_mse),
           Model = c("Traits","Traits","Traits",
                     "Traits+Descriptors","Traits+Descriptors","Traits+Descriptors",
                     "Descriptors","Descriptors","Descriptors"),
           Treatment = "Predator")

ggplot(mse_data_p, aes(x = Site, y = MSE, fill = Model))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_bw() + ggtitle("Predator")

mse_data_full <- rbind(mse_data_p, mse_data_f, mse_data_i, mse_data_h)

ggplot(mse_data_full, aes(x = Site, y = 1/MSE, fill = Model))+
  geom_bar(stat = 'identity', position = 'dodge')+
  theme_bw() + facet_wrap(~Treatment)

# ggplot(mse_data_full, aes(x = Site, y = MSE, fill = Treatment))+
#   geom_bar(stat = 'identity', position = 'dodge')+
#   theme_bw() + facet_wrap(~Model, scales='free')

@@

# 2.1 Remove SLA
anova(full.model, just.water.quadratic) # Full model is significanlty better

# 2.2 Remove herbivory
anova(full.model, just.sla.quadratic) # Full model still better

# 4. Quadratic vs linear
anova(full.model, all.linear) # Full model still better

# 5. Interaction reduction
anova(full.model, full.model.noint) # Full model still better
```

@@

tab_model(p.mod, i.mod, h.mod, f.mod,
          pred.labels = c("Intercept", 
                          "Log[SLA]-linear", 
                          "Numba", 
                          "Yawan",
                          "Log[SLA]-quadratic", 
                          "Water content - linear", 
                          "Water content - quadratic",
                          "Species richness",
                          "Abundance",
                          "Plasticity in SLA",
                          "Plasticity in WTR.C",
                          "Log[SLA]-linear : Numba",
                          "Log[SLA]-linear : Yawan",
                          "Log[SLA]-quadratic : Numba",
                          "Log[SLA]-quadratic : Yawan",
                          "Water content-linear : Numba",
                          "Water content-linear : Yawan",
                          "Water content-quadratic : Numba",
                          "Water content-quadratic : Yawan"),
          string.ci = "Conf. Int (95%)",
          string.p = "P-Value")
